ERNIE: A Knowledge Platform to Support Research Assessment

### 2017-12-26 LaTeX/Paper2/paper2.tex
update

In demonstration that is focused on the theme of data mining and network analysis, we have used the data within ERNIE to conduct seven case studies. In these studies, we mine and analyze data from policy documents, regulatory approvals, research grants, bibliographic and patent databases, and clinical trials, to document collaborations and identify influential research accomplishments. The workflows used incorporate expert knowledge into defining a set of core documents from which citations can be extracted, linked to other records in ERNIE, and analyzed. The first two case studies serve to validate ERNIE through reproducing the results of prior studies~\cite{Williams2015} on ivacaftor and ipilimumab, breakthrough drugs used to treat cystic fibrosis and melanoma. The remaining case studies concern drugs used to treat opioid addiction~\cite{Blumberg1973,Cowan1977} , a microarray system for pharmacogenomic profiling~\cite{deLeon2006}, a target discovery system originating from enzyme fragment complementation assays~\cite{Khanna1989}, and a behavioral intervention for substance abuse~\cite{Botvin1980}. The datasets that result from these studies are made available for use by other researchers and the workflows used to generate them are also archived to permit reproduction of our results, as well as review and modification of the methods used to generate them.

@@

\emph{Open Source} All ERNIE code is open-source under the MIT license and available on GitHub ~\cite{GithubERNIE2017}.

\emph{Infrastructure} ERNIE runs on two CentOS 7.4 Linux servers in the Microsoft Azure cloud with 10 terabytes of
attached storage.
One server, Azure standard D8s v3 (8 VCPUs, 32 Gb RAM), hosts data in a PostgreSQL 9.6 relational database, and
additionally acts as a central hub for data related processes.
A second server, an Azure standard DS4 (8 VCPUs, 28 Gb), runs Apache Solr 7.x search server, which is used to to create
and store indexes of ERNIE data to facilitate fast free-text user searches.
Access to ERNIE servers is secured through SSH tunneling and two-factor authentication, with a unique time-based code
acting as one of the factors.

Automated ERNIE processes are managed by the Jenkins Continuous Integration server.
Custom Extract-Transform-Load (ETL) scripts are developed in Bash, Python, Java and SQL.
Jenkins is additionally used to deploy scripts dedicated to data transformation and perform other
calculations.
In that regard, Jenkins is used to direct construction of Solr indexes as new data is introduced into
ERNIE, as well as the construction of citation networks for specified topics.
The Solr indexes can handle varying forms of Lucene-based search and full-text search, and may quickly return
informative, ranked, and scored query results so that a user may be able to map data across sources.
The citation networks are sub-networks (based largely in the Web of Science) that are generated based upon user input
and subsequently analyzed.

\emph{Data sources} Data in ERNIE are extracted from both publicly available and commercial sources. Publicly available data are copied from the National Clinical Trials Database \cite,  the FDA Orange and Purple Books \cite,  the United States Patent Office \cite, and NIH ExPORTER \cite. Leased data are acquired from Clarivate Analytics and consist of the Web of Science Core Collection and the Derwent World Patent Index~\cite{DWPI2017}. The data in ERNIE are stored in a relational schema that is documented. Documentation is available on GitHub.

\emph{Data architecture and governance} ERNIE is aiming to provide data of best possible quality to
its analysts and users.
ERNIE data is extracted from several upstream sources of varying quality hence the need to cleanse
data.
ERNIE's approach to cleansing is to prefer data quality and normalized data over data completeness.
The following are key aspects of ERNIE's data architecture and governance:
\begin{itemize}
  \item De-duplication.
De-duplication is a process of eliminating logically duplicate records, that is records with
identical primary or unique keys.
In ERNIE duplicate records from such a group are deleted while leaving in place a single
representative record (preferring a record which is updated last).
An alternative de-duplication strategy could be to aggregate differing non-key fields from logical
duplicates into lists.
  \item Normalization.
After data is de-duplicated, the next step in data normalization is to establish foreign key
relationships between children and parent entities and eliminate orphans: child records with
non-existing parents.
In ERNIE orphan records are deleted.
An alternative normalization strategy could be to segregate orphans logically or physically while
creating parent stub records.
  \item Schema Permanence.
In order to improve availability of data and simplify data schema management, ERNIE ETL scripts are
designed to avoid recreating of main entities, for example, by using TRUNCATE TABLE instead of table re-creation.
  \item Data Stewardship.
ERNIE data stewards are people responsible for quality of a particular data subject area.
Data stewards get notified when a data issue is detected and drive the workflows necessary for data
issue remediation.
They are also typically responsible for communicating changes in data structures.
\end{itemize}

\emph{Data mining and digitization} A set of source documents relevant to the question being asked is assembled and mined for citations to scientific literature using manual or semi-automated methods. Manual extraction involved searching for text strings that represent references of interest and matching those to unique identifiers in PubMed and/or Web of Science. As an example, the medical review document relevant to approval of ipilimumab contained X references. Y of them were matched to PubMed identifiers using the PubMed either through its web interface or the E-utils API. ERNIE is designed to support semi-automated case studies.

@@

\emph {Source document identification}

\emph {Citation extraction} Input and end product

@@

\section*{Results and Discussion}
\section*{Acknowledgments} Research and development reported in this publication was supported by Federal funds from the National Institute on Drug Abuse, National Institutes of Health, US Department of Health and Human Services, under Contract No. HHSN271201700053C. The content of this publication is solely the responsibility of the authors and does not necessarily represent the official views of the National Institutes of Health.

>>>>

In demonstration that is focused on the theme of data mining and network analysis, we have used the data within ERNIE to conduct seven case studies. In these studies, we mine and analyze data from policy documents, regulatory approvals, research grants, bibliographic and patent databases, and clinical trials, to document collaborations and identify influential research accomplishments. The workflows used incorporate expert knowledge into defining a set of core documents from which citations can be extracted, linked to other records in ERNIE, and analyzed. The first two case studies serve to validate ERNIE through reproducing the results of prior studies~\cite{Williams2015} on ivacaftor and ipilimumab, breakthrough drugs used to treat cystic fibrosis and melanoma. The remaining case studies concern two drugs used to treat opioid addiction~\cite{Blumberg1973,Cowan1977} , a microarray system for pharmacogenomic profiling~\cite{deLeon2006}, a target discovery system originating from enzyme fragment complementation assays~\cite{Khanna1989}, and a behavioral intervention for substance abuse~\cite{Botvin1980}. The datasets that result from these studies are made available for use by other researchers and the workflows used to generate them are also archived to permit reproduction of our results, as well as review and modification of the methods used to generate them.

@@

\emph{Infrastructure} ERNIE runs on two CentOS 7.4 Linux servers in the Microsoft Azure cloud with 10 terabytes of attached storage. One server, Azure standard D8s v3 (8 VCPUs, 32 Gb RAM), hosts data in a PostgreSQL 9.6 relational database, and additionally acts as a central hub for data related processes. A second server, an Azure standard DS4 (8 VCPUs, 28 Gb), runs Apache Solr 7.1 search server, which is used to to create and store indexes of ERNIE data to facilitate fast free-text user searches. Access to ERNIE servers is secured through SSH tunneling and two-factor authentication, with a unique time-based code acting as one of the factors.

\emph{Data sources} Data in ERNIE are extracted from both publicly available and commercial sources. Publicly available data are copied from the National Clinical Trials Database \cite,  the FDA Orange and Purple Books \cite, the United States Patent Office \cite, and NIH ExPORTER \cite. Leased data are acquired from Clarivate Analytics and consist of the Web of Science Core Collection and the Derwent World Patent Index~\cite{DWPI2017}. The data in ERNIE are stored in a relational schema that is documented. Documentation is available on GitHub. Custom Extract-Transform-Load (ETL) scripts are developed in Bash, Python, Java and SQL. Automated processes are managed by the Jenkins Continuous Integration server, which is additionally used to deploy scripts dedicated to data transformation, direct construction of Solr indexes as new data is introduced into ERNIE, and build citation networks for case studies. Solr indexes can handle varying forms of Lucene-based search and full-text search, and quickly return informative, ranked, and scored query results so that a user may be able to map data across sources. The citation networks are sub-networks (based largely in the Web of Science) that are generated based upon user input and subsequently analyzed. All ERNIE code is shared as open-source under the MIT license and is available on GitHub ~\cite{GithubERNIE2017}.

\emph{Data architecture and governance} ERNIE data is extracted from several upstream sources of varying quality and the  approach to cleansing is to prefer data quality and normalized data over data completeness. The following are key aspects of ERNIE's data architecture and governance. (i) De-duplication to eliminate logically duplicate records, that is records with identical primary or unique keys. In ERNIE duplicate records from such a group are deleted while leaving in place a single representative record (preferring a record which is updated last) (ii) Normalization to establish foreign key relationships between children and parent entities and eliminate orphans: child records with non-existing parents. )iii) Schema permanence to improve availability of data and simplify data schema management (iv) Data Stewardship to assign responsibility for quality of a particular data subject area. Data stewards are notified when a data issue is detected and drive the workflows necessary for data issue remediation. They are also typically responsible for communicating changes in data structures.

@@

\emph {Source document identification} A set of source documents relevant to the question being asked is assembled and mined for citations to scientific literature using manual or semi-automated methods.

\emph {Citation extraction and matching} Manual extraction involves searching for text strings that represent references of interest and matching those to unique identifiers in PubMed and/or Web of Science. For example, the medical review document relevant to approval of ipilimumab contained X references. Y of them were matched to PubMed identifiers using the PubMed either through its web interface or the E-utils API. ERNIE is designed to support semi-automated case studies.

@@

\section*{Results and Discussion}

Fig. 1 -Architecture

Table 1- List of Case Studies

Table 2- seedset, cited references, grants, etc for all 7

Table 3- NIH support- other support from WoS?

Figure 1-

What can we say about substance abuse and opioid addiction.

\section*{Acknowledgments} Research and development reported in this publication was supported by Federal funds from the National Institute on Drug Abuse, National Institutes of Health, US Department of Health and Human Services, under Contract No. HHSN271201700053C. The content of this publication is solely the responsibility of the authors and does not necessarily represent the official views of the National Institutes of Health.
